Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-15 paper/paper.tex
Mostly complete Features section

Every fault prediction study used some sort of machine learning algorithm as the heart of the model. There are a variety of ML algorithms including regression, neural networks, support vector machines, and decision trees.

\subsection{Regression}
Regression is a ML algorithm for data that can be fitted to a curve. A total of X papers use some form of regression (\cite{Posnett}, \cite{Rahman}, ...). Regression algorithms are considered to be the simplest type, but can perform well if the data can be well fitted to some sort of line or curve.

\subsection{Neural Networks}
Neural networks are designed to model the learning pattern of the human brain. Essentially, neural networks consist of nodes connected by links. The more a link is activated during training, the stronger it becomes and the more likely it will be selected during testing.

Jun Zheng \cite{zheng2010} used a back propagation neural network (BPNN) with AdaBoost, a way to achieve better classification results by producing diverse base classifiers. Zheng states that he used neural networks because they are popular in pattern recognition and BPNNs because they were the most frequent neural network used in the literature. AdaBoost was chosen because it is a popular way to improve the performance of the model.

\subsection{Other ML Algorithms}
Vandecruys et al \cite{Vandecruys} used a novel algorithm known as AntMiner+, which is based on Ant Colony Optimization which models the foraging behavior of ant colonies.

Tian Jiang's algorithm \cite{Jiang} was based on a classification scheme known as Personalized Change Classification+ (PCC+).

Nam et al \cite{Nam} implemented TCA+, which is a novel feature extraction technique for transfer learning with improved normalization.

\subsection{Discussion}
Catal et al \cite{Catal} suggested that more models be based on machine learning techniques rather than statistical methods or expert based systems. We see that research has followed the advice of the authors. Arisholm et al \cite{Arisholm} did not find any major differences among the different machine learning techniques, although they found that C4.5 with Adaboost gave the best results.

Not only have authors used well-known ML algorithms, but they have even implemented new ones. This shows that ML algorithms were the primary choice of recent studies and still are today.

@@

Even though the methodology is fairly standard throughout the papers we read, what actual metric is reported between precision, recall, overall accuracy, and F-Measure has considerable variance between papers.  One suggestion in \cite{Hall} is to present the confusion matrix itself rather than to present one statistic or the other when possible (where possible is determined by the sheer number of confusion matrices that would be produced).  The idea is that it would better enable comparison across studies since researchers could produce whatever statistic they happen to need from the data itself.

@@

 Arisholm et al use an area calculation that is normalized to be a proportion of the optimal area under the curve.  To find an approximation of the optimal cost effectiveness they use a ranking that puts the most error filled classes towards the front and then create a cost effectiveness line according to that ranking.  The actual calculation is $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/ (CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.  The same concept is also used by Rahman et al under the name AUCEC \cite{Rahman}.

@@

>>>>

@@

Even though the methodology is fairly standard throughout the papers we read, what actual metric is reported between precision, recall, overall accuracy, and F-Measure has considerable variance between papers.  The Vandecruys paper \cite{Vandecruys} even uses terminology that is separate from many other publications in using sensitivity for recall and specificity for the true negative rate, which is a seldom reported statistic. One suggestion in \cite{Hall} is to present the confusion matrix itself rather than to present one statistic or the other when possible (where possible is determined by the sheer number of confusion matrices that would be produced).  The idea is that it would better enable comparison across studies since researchers could produce whatever statistic they happen to need from the data itself.

@@

 Arisholm et al use an area calculation that is normalized to be a proportion of the optimal area under the curve.  To find an approximation of the optimal cost effectiveness they use a ranking that puts the most error filled classes towards the front and then create a cost effectiveness line according to that ranking.  The actual calculation is\\ $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/$\\ $(CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.  The same concept is also used by Rahman et al under the name AUCEC \cite{Rahman}.

@@

This section could also be labeled metrics, as it is in many places throughout the literature on this topic, but to not confuse it and the previous section on evaluation metrics we have chosen to label it features.  The main reasoning for this is the fact that metrics are actually used as features in this area and not actually as metrics for comparison of one method versus another.  The Radjenovic paper \cite{Radjenovic} is a fairly exhaustive paper with relation to metrics/features in fault prediction.  Radjenovic came up with three categories to discuss in their literature review, and we will stick with those same categories in relation to the papers we reviewed.  The categories are: Traditional, Object-Oriented, and Process.  Some of the papers we reviewed defy this categorization and use metrics that are either one offs or are hybridized to such a degree that they should be explained on their own.

\subsection{Traditional}

These are metrics that relate to complexity (ie McCabe or Halstead calculations) and lines of code.  A good number of papers we reviewed used these metrics as feature \cite{Posnett} \cite{Vandecruys} \cite{Bird}.  There is considerable discussion in terms of whether these sorts of metrics provide good quality models or not.  Hall et al indicate that in their review that models using only static code metrics that are complexity based have poor performance, but that Lines of Code based models tend to be useful \cite{Hall}.  Radjenovic et al indicate that LOC has no strong evidence behind it in terms of faults furthermore they state that smaller studies in general have given more weight to LOC and size metrics than larger studies, because of that they rated the effectiveness of the metric as "moderate"\cite{Radjenovic}.  On complexity metrics Radjenovic states that these metrics are reasonable, but that "others are better"\cite{Radjenovic}.

\subsection{Object Oriented Metrics}

Object oriented metrics seem to have been dominated by the metrics presented by Chidamber and Kemerer \cite{Chidamber} \cite{DAmbros}.  These metrics include things like number of children(NOC), coupling between classes (CBO), or lack of cohesion of methods (LCOM).    Object oriented metrics were used in only one of our papers, Arisholm et al, and used there really only as a comparison metric\cite{Arisholm}.  In terms of evaluation of their success or failure Radjenovic et al indicate that OO metrics are useful but that there is some debate about whether OO metrics and size are correlated and that further work is needed in that area  \cite{Radjenovic}.  Hall et al state that OO and LOC are actually on pretty equal footing and that OO provides better performance than source code metrics \cite{Hall}.

\subsection{Process Metrics}

Process metrics relate to things like number of developers, code churn, number of commits, features, etc.  Process metrics are mostly mined from source code management systems like Git, and also bug tracking and issue tracking systems like Jira.   These metrics have a strong following in the fault prediction community and are well represented in our papers \cite{Posnett} \cite{Bird} \cite{Arisholm} \cite{Rahman}.  Rahman et al particularly only used a set of process metrics while the other papers mentioned used some sort of combination of process and other metrics.  There is some dispute between Radjenovic and Hall with regards to process metrics, with Hall suggesting that their performance was the worst out of everything they had examined where Radjenovic considers process metrics to be promising and that they are deserving of further study and validation while additionally stating that they provide superior post-release fault prediction \cite{Hall} \cite{Radjenovic}.

\subsection{Organizational Structure}
This is an approach that was proposed by Nagappan et al at Microsoft Research \cite{Nagappan}.  The metrics included a set of 8 measures of organizational complexity: Number of engineers, Edit Frequency, Depth of Master Ownership, Percentage of Org contributing to development, Overall Organization Ownership, and Organization Intersection Factor.  They used these metrics to create a fault prediction model and compared its performance in Precision and recall against a set of OO, Traditional, and Process metrics.  For Windows Vista they show that Organizational metrics are superior to the other types of metrics available.  As mentioned in the paper there are questions about whether this approach would work outside Microsoft or with a smaller project.

Naggapan and Bird produced another paper in the next year using organizational metrics again with a bit of a twist in looking at whether distributed development had an effect on software quality \cite{Bird}.  This paper added an additional metric of the actual location of the members of teams working on Windows Vista with levels starting at the same building and growing to the point of developers working at locations across the globe from one another.  Organizaitonal metrics as well as a set of process and traditional metrics were used in conjunction with the distribution metric seemingly out of surprise that there was little difference between distributed projects and more local projects.  The idea was to try to prove that there was not in fact some correlation between the other metrics they looked at and the performance of teams across long distances.  They found that in fact there was no difference and that distributed development within one company was possible without sacrificing quality.
